Untrusted B2B Collaboration using the Blockchain

### 2018-07-30 paper/paper.tex
Minor stuff
gas costs and rephrasing

\section{Solution Approach} \label{solutionapproach}
We propose a system design, that allows choreographies to be executed publicly on the blockchain.
In the following section, we describe our approach and its architecture.

@@

The recursive initialization ensures that all instance contracts that are part of the process instance will be created by one function call.
%TODO add emit event in the diagram
%TODO rephrasing
The organizations that did not start the instance creation can detect the new process instance by using their trigger to watch the factory contract.

@@

\begin{figure}
	\centering
\includegraphics[width=0.9\textwidth]{fig/Armadillo.png}
\caption{Screenshot of the Armadillo web application.}
\label{fig:armadillo}
\end{figure}

@@

\begin{table}
	\centering
	\caption{Gas used by contracts in the example choreography.} \label{gasusage}
	\begin{tabular}{|l | c | c | c|}
		\hline                          & \textbf{Factory} & \textbf{Instance} & \textbf{Sum}       \\
		\hline \textbf{Bulk Buyer}      & 4,590,569        & 59,396            & 4,649,965          \\
		\hline \textbf{Manufacturer}    & 129,588          & 124,316           & 253,904            \\
		\hline \textbf{Middleman}       & 129,586          & 111,189           & 240,775            \\
		\hline \textbf{Supplier}        & 86,398           & 61,745            & 148,143            \\
		\hline \textbf{Special Carrier} & 86,376           & 81,945            & 168,321            \\
		\hline \textbf{Sum}             & 5,022,517        & 438,591           & \textbf{5,461,108} \\ \hline
	\end{tabular}
\end{table}
% TODO add exchange rates and $ price? or propmt users to look it up themselves because of changing gas price?
Most of the transactions have proven to come with reasonable gas costs.
However, the instantiation cost that is currently paid by the initiator appears to be problematic.
As the first instantiation transitively triggers all the other participant's instantiations, this can become quite costly, and might even surpass the \emph{block gas limit}, the maximum amount of gas that can be spent per new block, depending on the number of participants involved.
%Even if that is not the case, a high gas cost is still a problem, since in Ethereum, by design, transactions with high gas costs are less likely to be included in a block by miners, possibly leading to long waiting times. % TODO why again?

>>>>

\section{Solution Approach} \label{solutionapproach}

@@

The recursive initialization ensures that all instance contracts that are part of the process instance will be created by one function call.
%TODO add emit event in the diagram
All other organizations can detect the created instances by watching the factory contract, using a trigger.

@@

\begin{figure}
	\centering
\includegraphics[width=\textwidth]{fig/Armadillo.png}
\caption{Screenshot of the Armadillo web application.}
\label{fig:armadillo}
\end{figure}

@@

\begin{table}
	\centering
	\caption{Gas used by contracts in the example choreography.} \label{gasusage}
	\begin{tabular}{|l | c | c | c|}
		\hline                          & \textbf{Factory} & \textbf{Instance} & \textbf{Sum}       \\
		\hline \textbf{Bulk Buyer}      & 4,590,569        & 59,396            & 4,649,965          \\
		\hline \textbf{Manufacturer}    & 129,588          & 124,316           & 253,904            \\
		\hline \textbf{Middleman}       & 129,586          & 111,189           & 240,775            \\
		\hline \textbf{Supplier}        & 86,398           & 61,745            & 148,143            \\
		\hline \textbf{Special Carrier} & 86,376           & 81,945            & 168,321            \\
		\hline \textbf{Sum}             & 5,022,517        & 438,591           & \textbf{5,461,108} \\ \hline
	\end{tabular}
\end{table}
Because of highly fluctuating exchange rates of USD to ether and ether to gas, the total gas cost varies as well. At the time of writing the total cas cost amounted to \$2.50 according to \url{ethgasstation.info}. 
Most of the transactions have proven to come with reasonable gas costs.
However, the instantiation cost that is currently paid by the initiator appears to be problematic.
As the first instantiation transitively triggers all the other participant's instantiations, this can become quite costly, and might even surpass the \emph{block gas limit}, the maximum amount of gas that can be spent per new block, depending on the number of participants involved.
%Even if that is not the case, a high gas cost is still a problem, since in Ethereum, by design, transactions with high gas costs are less likely to be included in a block by miners, possibly leading to long waiting times. % TODO why again?
